%-------------------------
% Resume in Latex
% Author : Akash Dubey
% Tailored for Research Engineer (industry): Emphasizing research-to-code, CUDA/HPC, large-scale experiments, model training/fine-tuning, benchmarking, and reproducibility across domains
%------------------------
\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}
% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1
%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
%-------------------------------------------
%%%%%% RESUME STARTS HERE %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%----------HEADER----------
\begin{center}
    \textbf{\Huge \scshape Akash Dubey} \\ \vspace{1pt}
    \small (212)-814-3681 $|$ \href{mailto:akashdub06@gmail.com}{\underline{akashdub06@gmail.com}} $|$
    \href{https://akashdubey.me/}{\underline{akashdubey.me}} $|$
    \href{https://github.com/AkeBoss-tech}{\underline{github.com/AkeBoss-tech}} $|$
    \small U.S. Citizen
\end{center}
%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Rutgers University Honors College, School of Arts and Sciences}{New Brunswick, NJ}
      {Bachelor of Science in Computer Science and Mathematics}{Anticipated May 2027}
      \resumeItemListStart
        \resumeItem{\textbf{GPA}: 3.95/4.0 $|$ SAT: 1580}
        \resumeItem{\textbf{Relevant Coursework}: Tensor Networks, Systems Programming, Stochastic Processes, Computer Architecture, Algorithms, Data Structures, Honors Calculus III \& IV, Math Theory of Probability.}
        \resumeItem{\textbf{Academic Programs \& Research}: Directed Research Reading Program on Symmetric Functions (representation theory for combinatorial optimization); Physics Learning Theory Seminar (statistical mechanics in high-dimensional learning), Dean's List.}
        \resumeItem{\textbf{Activities}: Quantitative Finance Club, Road to Silicon Valley Program (Cohort 6), ESL Instructor, Pickleball.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
%-----------AI/ML RESEARCH-----------
\section{Research}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Algorithmic Robotics and Control Lab in Rutgers's Dept. of CS}{New Brunswick, NJ}
      {Research Assistant (Advisor: Prof. Jingjin Yu)}{Jan 2026 -- Present}
      \resumeItemListStart
        \resumeItem{Implemented and validated CUDA versions of pRRTC and FCIT*, parallelizing tree/graph search and collision checking for high-dimensional ASAO robot motion planning across 500 benchmark problems.}
        \resumeItem{Developing a graph-based search policy (GaP) for dual-arm task-and-motion planning (TAMP), learning from successful and failed planner traces to rank symbolic action skeletons and predict geometric feasibility. Working in Isaac Sim specifically in dual-arm motion planning to further bridge TAMP capabilities with ML.}
      \resumeItemListEnd
    \resumeSubheading
        {Kwan Lab, Rutgers Cancer Institute of New Jersey}{New Brunswick, NJ}
        {Computational Biology Research Assistant (Advisor: Prof. Kelvin Kwan)}{Jan 2026 -- Present}
        \resumeItemListStart
            \resumeItem{Configured and validated a reproducible DeepSTARR inference environment, resolving legacy TensorFlow/Keras dependencies on HPC to enable sequence-based prediction of developmental and housekeeping enhancer activity.}
            \resumeItem{Developed an AlphaGenome-based in silico deletion screen spanning 12 candidate sites, 3 deletion sizes (10, 40, and 80 kb), and 2 cell types (72 perturbation conditions) to quantify TAD-boundary sensitivity; identified a chr12 insulator with the strongest predicted insulation loss among 12 candidates.}
            \resumeItem{Built a 3D chromatin polymer simulator using overdamped Langevin dynamics to generate conformations from Hi-C contact matrices; implemented multi-scale TAD detection using insulation score and directionality index methods and validated the pipeline with 70+ automated tests.}
    \resumeItemListEnd
  \resumeSubheading
      {\href{https://rutgerseconomics.org}{Rutgers Economics Labs}}{New Brunswick, NJ}
      {President (formerly Research Director, Team Lead)}{Oct 2024 -- Present}
      \resumeItemListStart
        \resumeItem{Architected an AI automated economic research pipeline RAIL (Rutgers Agentic Intelligence Labs) to collect, organize, analyze, and synthesize economic data to derive insights using data ontologies and coding agent workflows.}
        \resumeItem{Leading quantitative research projects for partners including NJDOL, NJDEP, NJBPU, Federal HUD, U.S. Census Bureau; applied econometric models in Python/R to analyze large datasets and project economic trends.}
        \resumeItem{Previously led a team of five researchers to evaluate the efficacy of the Urban Enterprise Zone program for the NJDCA, utilizing econometric methods in R and Python to analyze complex census datasets.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
%-----------EXCEPTIONAL TECHNICAL PROJECTS-----------
\section{Selected Technical Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\href{https://github.com/AkeBoss-tech/llm-research}{\textbf{SLM Optimization \& Post-Training (GSM8k)}} $|$ \emph{PyTorch, HPC, Quantization, Pruning}}{}
          \resumeItemListStart
            \resumeItem{Fine-tuned small language models (SLMs) on the GSM8k math reasoning dataset to study the effects of different model sizes and architectures on math reasoning capabilities.}
            \resumeItem{Deployed models on the Rutgers High Performance Computing (Amarel) cluster, utilizing quantization and structural pruning to maximize inference throughput on constrained compute.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\href{https://github.com/AkeBoss-tech/knowledge}{\textbf{Knowledge Base and AI Agent Workflow Manager}} $|$ \emph{Data Ontology, Workflows, Coding Agents} }{}
          \resumeItemListStart
            \resumeItem{Built KRAIL (pypi), a local-first, repo-backed knowledge runtime that structures raw notes into ontology-aware topic pages, markdown graphs, source ledgers, claim records, verification runs, and artifact lineage for evidence-grounded agent memory.}
            \resumeItem{Implemented MCP/CLI and agent infrastructure for auditable coding-agent workflows (for software factories, auto-research, and company brain use cases), including local runner dispatch, dry-run work orders, session logs, role prompts/checklists, workflow validation, and hybrid keyword-graph-vector retrieval.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Local Coworker: Native macOS Computer-Use Agent} $|$ \emph{Swift, MCP, Gemini Vision} (private code)}{}
          \resumeItemListStart
            \resumeItem{Built a native desktop agent capable of autonomous computer use by integrating Gemini Vision with macOS Accessibility APIs, AppleScript, and JXA.}
            \resumeItem{Implemented the Model Context Protocol (MCP) to orchestrate specialized sub-agents (UI Interaction, Shell, App Research) for planning and executing complex multi-app workflows.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd
%-----------ENGINEERING EXPERIENCE-----------
\section{Engineering Experience}
  \resumeSubHeadingListStart
  \resumeSubheading
      {\href{https://newyorklife.com/}{New York Life Insurance}}{New York, NY}
      {Software Engineer Intern, TDAV Team}{May -- Aug 2026}
      \resumeItemListStart
        \resumeItem{Created an AI text and voice agent for processing insurance claims for clients and 12,000 Customer Service Representatives using AWS Infrastructure with access to NYL services, knowledge, and forms.}
        \resumeItem{Constructed a company wiki/knowledge base from 13,000 documents compiled from Sharepoint, Public Site, Confluence, Jira, and the Intranet bringing business logic into one place for AI and human users.}
      \resumeItemListEnd
    \resumeSubheading
  {\href{https://getlykke.com/}{Lykke}}{San Francisco, CA}
  {Founding Software Engineer}{Sep 2025 -- Present}
  \resumeItemListStart
    \resumeItem{Built core AI workflows for an AI study platform used to ingest Canvas LMS courses, assignments, announcements, notes, and uploaded documents into class-scoped knowledge bases for contextual chat and study generation.}
    \resumeItem{Engineered adaptive RAG pipelines across MongoDB, Zilliz/Milvus, S3, Gemini Files API, and SSE streaming, including source inference, citation events, token-budgeting for large course materials, and fallback paths for extracted text vs. full-file reasoning.}
  \resumeItemListEnd
    \resumeSubheading
      {\href{https://scarletsync.app/}{Scarlet Sync}}{New Brunswick, NJ}
      {Founder}{Jan 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Architected a robust data ingestion pipeline using Python and LLMs to reverse-engineer legacy data, indexing over 2,500 classes and 500+ degree programs for real-time querying.}
        \resumeItem{Developed a production AI assistant with streaming tool-calling and grounded retrieval over schedules, degree plans, and profile context, enabling automated schedule building and personalized academic planning across Web, ChatGPT, Claude, and iOS.}
      \resumeItemListEnd
    \resumeSubheading
      {\href{https://www.samaritanscout.org/}{Samaritan Scout}}{Cranford, NJ}
      {Full Stack Engineer Intern}{May 2023 -- Aug 2025}
      \resumeItemListStart
        \resumeItem{Developed an agentic scraping system leveraging OpenAI and Gemini structured outputs to autonomously extract data from over 100,000 non-profit websites, reducing manual data entry time by over 90\%.}
        \resumeItem{Developed a full-stack search engine using React, TypeScript, and PostgreSQL to index 35,000+ volunteer opportunities, implementing semantic search algorithms with hallucination filters to ensure accurate matching.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
%-----------AWARDS \& SKILLS-----------
\section{Awards \& Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Awards}{: \href{https://github.com/AkeBoss-tech/top-coder-challenge}{8090 AI Top Coder (5th)}, Rutgers Shark Tank (2nd and 3rd), \href{https://acashmoney.biz/portfolio/asa-fall-data/}{ASA Fall Data Challenge (Top 3)}, NSF I-Corps.} \\
     \textbf{Languages}{: Python, C++, CUDA, Java, SQL, TypeScript, R, Bash, Git} \\
     \textbf{Technologies}{: PyTorch, CUDA, Transformers, Quantization \& Pruning, HPC Clusters, Generative AI, Agents, Scikit-learn, Pandas, AWS}
    }}
 \end{itemize}
\end{document}
